Descriptive, not injunctive, social norms caused increases in mask wearing during the COVID-19 pandemic

### 2023-03-15 manuscript.Rmd
update manuscript

Research has investigated how social norms emerge in a population over time. In the long term, cultural evolutionary models show that injunctive social norms can be vertically transmitted across generations by imitation or teaching, or horizontally diffused from neighboring populations [@Henrich2015]. However, less is known about how social norms arise endogenously within populations in the short term, including how descriptive norms arise and interact with injunctive norms to shape behavior. Recent work in behavioral economics suggests that social norms of public good provisioning develop in tandem with cooperative behavior through repeated interactions [@Titlestad2019]. But it remains unclear whether these findings generalize beyond the laboratory to real human populations.

>>>>

Research has investigated how social norms emerge in a population over time. In the long term, cultural evolutionary models show that injunctive social norms can be vertically transmitted across generations by imitation or teaching, or horizontally diffused from neighboring populations [@Henrich2015]. However, less is known about how social norms arise endogenously within populations in the short term. While researchers have simulated the emergence of descriptive norms [@Muldoon2014a;@Muldoon2014b], this modelling work does not capture how descriptive norms develop alongside injunctive norms in real-world settings. Recent work in behavioral economics has also suggested that injunctive norms of public good provisioning develop in tandem with cooperative behavior through repeated interactions [@Titlestad2019]. But it remains unclear whether these findings generalize beyond the laboratory to real human populations.
